\acknowledgments {First and foremost, I would like to express my sincere gratitude to my advisor, Prof. Bahram Jalali, for his immeasurable amount of support and guidance. His patience, vast and deep knowledge of numerous fields, and attention to fundamentals have always inspired me. His training has significantly influenced my character both in professional and personal life. 

Wholeheartedly, I thank Prof. Kayvan R. Niazi. His knowledge, his passion for teaching, and above all, his spirit has been inspirational. His insightful feedback and guidance, specifically on biological studies were critical in completing this work. Also, I would like to thank my other committee members, Prof. Tatsuo Itoh, Prof. Katsushi Arisaka, Prof. Benjamin S. Williams, and Prof. Dean Ho, for their invaluable time and feedback.

I would like to thank impressive students and postdoctoral researchers of Prof. Jalali's research laboratory, who I have learned alot from. Specifically, Keisuke Goda and Daniel Solli had a significant influence on shaping me into a scientist. Also, I am very thankful to Eric Diebold, Kevin K. Tsia, Jost Adam, Ali Fard, Ali Ayazi, Niusha Sarkhosh, Kam Yan Hon, and Alexander Weidel for the helpful discussions that we had. I would like to express my appreciation for the help of our undergraduate students, especially Allen Huang, Li-Chia Tai, and Jim Lin who have dedicated significant amount of time and effort to my project. Last, but not least, I am truly grateful of my colleague graduate student, Claire Lifan Chen, who has worked with me through good and bad times of many projects. Without her help, I could have never achieved many of my celebrated results.

I would like to thank all of my publication co-authors, which our works consist many chapters of this dissertation, especially Prof. Shahrooz Rabizadeh, Prof. Dino Di Carlo, and Dr. Daniel Gossett. Chapter \ref{chp:APL2011_Chapter} is a version of Applied Physics Letters, Vol. 98, No. 10, 101107, 2011. Chapter \ref{chp:PW2013_Chapter} is a version of Proceedings of SPIE, Frontiers in Ultrafast Optics: Biomedical, Scientific, and Industrial Applications XIII, San Francisco, CA, 2013, 86110N, which is a collaborative work between Prof. Bahram Jalali and Prof. Dino Di Carlo's groups. Chapter \ref{chp:BOE2013_Chapter} is a version of Biomedical Optics Express, Vol. 4, No. 9, pp. 1618-1625, 2013. Chapter \ref{chp:JOSAA2013_Chapter} is a version of Journal of the Optical Society of America A, Vol. 30, No. 10, pp. 2124-2132, 2013. Finally, Chapter \ref{chp:CLEO2010_Chapter} is a version of Conference on Lasers and Electro-Optics (CLEO), San Jose, CA, 2010, CFA4.

I also had many great mentors over the course of my undergraduate education who led me to this PhD in Electrical Engineering. In particular, I am very grateful of Prof. Mahmoud Shahabadi, Prof. Mohammad Yavari, and Prof. Zainalabedin Navabi. 

Furthermore, I would like to thank my friends Yunan Zhu and Zohreh Khodaparast whose support gave me the strength, energy, and drive to go through difficulties of this program. Finally, I would like to thank my roommate, Arash Mirhaj for productive technical and non-technical discussions over many late night working hours. 

Most important of all, I am supremely grateful to my family for their unconditional love and support. They have sacrificed so much for me to be here. My mom, Azarjoun, has been my role model for being hardworking, reliable, and hopeful while I learned being thorough from my dad. My sister, Maryam has been a constant source of love, and My brother, Ali has always supported my curiosity... Azarjoun, Baba, Maryam, and Ali! You helped me whenever I needed it. Thank you for always being there.
}
