
\publication   {J. Chan, \textbf{A. Mahjoubfar}, M. Asghari, and B. Jalali, ``\textit{Reconstruction in time-bandwidth compression systems,}'' Applied Physics Letters, Vol. 105, No. 22, 221105, 2014.}

\presentation   {A. Yazaki, \textbf{A. Mahjoubfar}, C. Kim, J. Chan, K. Goda, M. Watanabe, and B. Jalali, ``\textit{Ultrafast web-inspecting laser scanner,}'' Progress In Electromagnetics Research Symposium, Guangzhou, China, 2014, 140319211016.}

\presentation   {\textbf{A. Mahjoubfar} and C. Chen, ``\textit{Intellectual property for dynamic algorithms and data visualization,}'' World Economic Forum's Global Agenda Council on the Intellectual Property System: The Intersection of Big Data and Intellectual Property in the 21st Century, University of Washington, Seattle, WA, 2014, Session IV.}

\presentation   {C. Chen, \textbf{A. Mahjoubfar}, A. Huang, K. R. Niazi, S. Rabizadeh, and B. Jalali, ``\textit{Hyper-dimensional analysis for label-free high-throughput imaging flow cytometry,}'' Conference on Lasers and Electro-Optics (CLEO), San Jose, CA, 2014, AW3L.2.}

\presentation   {C. Kim, \textbf{A. Mahjoubfar}, A. Yazaki, J. Chan, K. Goda, M. Watanabe, and B. Jalali, ``\textit{Ultrafast surface-inspecting laser scanner,}'' Far East Forum on Nondestructive Evaluation/Testing, Chengdu, China, 2014.\\
Recipient of the third-place award in the English division of the conference.}

\publication   {A. Yazaki, C. Kim, J. Chan, \textbf{A. Mahjoubfar}, K. Goda, M. Watanabe, and B. Jalali, ``\textit{Ultrafast dark-field surface inspection with hybrid-dispersion laser scanning,}'' Applied Physics Letters, Vol. 104, No. 25, 251106, 2014.}

\presentation   {C. Chen, \textbf{A. Mahjoubfar}, A. Huang, L. Tai, K. R. Niazi, S. Rabizadeh, and B. Jalali, ``\textit{Hyper-dimensional analysis for label-free high-throughput imaging flow cytometry,}'' XXIX Congress of the International Society for Advancement of Cytometry, Fort Lauderdale, Florida, 2014.}

\presentation   {J. Adam, \textbf{A. Mahjoubfar}, E. D. Diebold, B. W. Buckley, and B. Jalali, ``\textit{Time-stretched spectrally encoded angular light scattering for high-throughput real-time diagnostics,}'' Proceedings of SPIE, Biophotonics: Photonic Solutions for Better Health Care, Brussels, Belgium, 2014, 91291A-1.}

\presentation   {\textbf{A. Mahjoubfar}, C. Chen, K. R. Niazi, S. Rabizadeh, and B. Jalali, ``\textit{Label-free high-throughput imaging flow cytometry,}'' Proceedings of SPIE, Frontiers in Ultrafast Optics: Biomedical, Scientific, and Industrial Applications XIV, San Francisco, CA, 2014, 89720F.}

\publication   {J. Adam, \textbf{A. Mahjoubfar}, E. D. Diebold, B. W. Buckley, and B. Jalali, ``\textit{Spectrally encoded angular light scattering,}'' Optics Express, Vol. 21, No. 23, pp. 28960-28967, 2013.\\
Selected article for Virtual Journal for Biomedical Optics, Vol. 9, No. 1, 2014.}

\publication   {\textbf{A. Mahjoubfar}, K. Goda, G. Betts, and B. Jalali, ``\textit{Optically amplified detection for biomedical sensing and imaging,}'' Journal of the Optical Society of America A, Vol. 30, No. 10, pp. 2124-2132, 2013.}

\presentation   {B. Jalali, E. Diebold, \textbf{A. Mahjoubfar}, B. Buckley, and K. Goda, ``\textit{Ultrahigh Throughput Single Cell Imaging,}'' Frontiers in Optics, Orlando, FL, 2013, FW1D.2.}

\publication   {\textbf{A. Mahjoubfar}, C. Chen, K. R. Niazi, S. Rabizadeh, and B. Jalali, ``\textit{Label-free high-throughput cell screening in flow,}'' Biomedical Optics Express, Vol. 4, No. 9, pp. 1618-1625, 2013.}

\presentation   {\textbf{A. Mahjoubfar}, K. Goda, C. Wang, A. Fard, J. Adam, D. R. Gossett, A. Ayazi, E. Sollier, O. Malik, E. Chen, Y. Liu, R. Brown, N. Sarkhosh, D. Di Carlo, and B. Jalali, ``\textit{3D ultrafast laser scanner,}'' Proceedings of SPIE, Frontiers in Ultrafast Optics: Biomedical, Scientific, and Industrial Applications XIII, San Francisco, CA, 2013, 86110N.}

\publication   {K. Goda, \textbf{A. Mahjoubfar}, C. Wang, A. Fard, J. Adam, D. R. Gossett, A. Ayazi, E. Sollier, O. Malik, E. Chen, Y. Liu, R. Brown, N. Sarkhosh, D. Di Carlo, and B. Jalali, ``\textit{Hybrid dispersion laser scanner,}'' Scientific Reports, Vol. 2, 445, 2012.\\
Highlighted in Nature Photonics, Vol. 6, No. 9, p. 573, 2012.}

\publication   {A. M. Fard, \textbf{A. Mahjoubfar}, K. Goda, D. R. Gossett, D. Di Carlo, and B. Jalali, ``\textit{Nomarski serial time-encoded amplified microscopy for high-speed contrast-enhanced imaging of transparent media,}'' Biomedical Optics Express, Vol. 2, No. 12, pp. 3387-3392, 2011.}

\presentation   {A. Fard, \textbf{A. Mahjoubfar}, K. Goda, and B. Jalali, ``\textit{Nomarski serial time-encoded amplified microscope for high throughput imaging of transparent media,}'' Conference on Lasers and Electro-Optics (CLEO), Baltimore, MD, 2011, CThW1.}

\presentation   {K. Goda, \textbf{A. Mahjoubfar}, A. Ayazi, A. Fard, S. H. Kim, and B. Jalali, ``\textit{High-speed nanometer-resolved imaging-based laser vibrometry,}'' Conference on Lasers and Electro-Optics (CLEO), Baltimore, MD, 2011, JWA78.}

\publication   {\textbf{A. Mahjoubfar}, K. Goda, A. Ayazi, A. Fard, S. H. Kim, and B. Jalali, ``\textit{High-speed nanometer-resolved imaging vibrometer \& velocimeter,}'' Applied Physics Letters, Vol. 98, No. 10, 101107, 2011.\\
Selected article for Virtual Journal of Nanoscale Science \& Technology, Vol. 23, No. 11, 2011 and Virtual Journal of Ultrafast Science, Vol. 10, No. 4, 2011.}

\presentation   {\textbf{A. Mahjoubfar}, K. Goda, and B. Jalali, ``\textit{Raman amplification at 800 nm in single-mode fiber for biological sensing and imaging,}'' Conference on Lasers and Electro-Optics (CLEO), San Jose, CA, 2010, CFA4.}

\publication   {K. Goda, \textbf{A. Mahjoubfar}, and B. Jalali, ``\textit{Demonstration of Raman gain at 800 nm in single-mode fiber and its potential application to biological sensing and imaging,}'' Applied Physics Letters, Vol. 95, No. 25, 251101, 2009.\\
Selected article for Virtual Journal of Ultrafast Science, Vol. 9, No. 1, 2010.}

\publication   {N. Talebi, \textbf{A. Mahjoubfar}, and M. Shahabadi, ``\textit{Plasmonic ring resonator,}'' Journal of the Optical Society of America B, Vol. 25, Issue 12, pp. 2116-2122, 2008.\\
Selected article for Virtual Journal of Nanoscale Science \& Technology, Vol. 19, No. 1, 2009.}
