
\presentation   {\textbf{A. Mahjoubfar} and C. Chen, ``\textit{Intellectual property for dynamic algorithms and data visualization,}'' World Economic Forum's Global Agenda Council on the Intellectual Property System: The Intersection of Big Data and Intellectual Property in the 21st Century, University of Washington, Seattle, WA, 2014, Session IV.}

\presentation   {\textbf{A. Mahjoubfar}, C. Chen, K. R. Niazi, S. Rabizadeh, and B. Jalali, ``\textit{Label-free high-throughput imaging flow cytometry,}'' Proceedings of SPIE, Frontiers in Ultrafast Optics: Biomedical, Scientific, and Industrial Applications XIV, San Francisco, CA, 2014, 89720F.}

\publication   {\textbf{A. Mahjoubfar}, K. Goda, G. Betts, and B. Jalali, ``\textit{Optically amplified detection for biomedical sensing and imaging,}'' Journal of the Optical Society of America A, Vol. 30, No. 10, pp. 2124-2132, 2013.}

\publication   {\textbf{A. Mahjoubfar}, C. Chen, K. R. Niazi, S. Rabizadeh, and B. Jalali, ``\textit{Label-free high-throughput cell screening in flow,}'' Biomedical Optics Express, Vol. 4, No. 9, pp. 1618-1625, 2013.}

\presentation   {\textbf{A. Mahjoubfar}, K. Goda, C. Wang, A. Fard, J. Adam, D. R. Gossett, A. Ayazi, E. Sollier, O. Malik, E. Chen, Y. Liu, R. Brown, N. Sarkhosh, D. Di Carlo, and B. Jalali, ``\textit{3D ultrafast laser scanner,}'' Proceedings of SPIE, Frontiers in Ultrafast Optics: Biomedical, Scientific, and Industrial Applications XIII, San Francisco, CA, 2013, 86110N.}

\publication   {\textbf{A. Mahjoubfar}, K. Goda, A. Ayazi, A. Fard, S. H. Kim, and B. Jalali, ``\textit{High-speed nanometer-resolved imaging vibrometer \& velocimeter,}'' Applied Physics Letters, Vol. 98, No. 10, 101107, 2011.\\
Selected article for Virtual Journal of Nanoscale Science \& Technology, Vol. 23, No. 11, 2011 and Virtual Journal of Ultrafast Science, Vol. 10, No. 4, 2011.}

\presentation   {\textbf{A. Mahjoubfar}, K. Goda, and B. Jalali, ``\textit{Raman amplification at 800 nm in single-mode fiber for biological sensing and imaging,}'' Conference on Lasers and Electro-Optics (CLEO), San Jose, CA, 2010, CFA4.}
